%===============================================================================
% $Id: ifacconf.tex 19 2011-10-27 09:32:13Z jpuente $  
% Template for IFAC meeting papers
% Copyright (c) 2007-2008 International Federation of Automatic Control
%===============================================================================
\documentclass{ifacconf}

\usepackage{natbib}        % required for bibliography

\input{head/pkgs.tex}
\input{head/defs.tex}
\input{head/glossaries}
\input{head/acronyms}
\input{figures/diagram.tex}

\usetikzlibrary{external}
\tikzexternalize
%===============================================================================
\begin{document}
\begin{frontmatter}

\title{Distributed Model Predictive Control of Centrifugal Compressor Systems} 
% Title, preferably not more than 10 words.

% \thanks[footnoteinfo]{Sponsor and financial support acknowledgment
% goes here. Paper titles should be written in uppercase and lowercase
% letters, not all uppercase.}

\author[First]{K. Jones} 
\author[First]{A. Cortinovis} 
\author[First]{M. Mercangoez}

\address[First]{ABB Switzerland Ltd., Corporate Research, Baden-Dättwil, Switzerland (e-mail: katie.jones@reactive-robotics.com, andrea.cortinovis@ch.abb.com, mehmet.mercangoez@ch.abb.com).}

\begin{abstract}                % Abstract of not more than 250 words.
The performance and computational cost of distributed MPC for the control of compressor networks is investigated in simulation.
Both cooperative and non-cooperative approaches are considered and compared to the performance achieved with centralized control in the presence of a discharge-side disturbance.
Two systems, each with two compressors, are studied: one is arranged in parallel configuration and the other in series.
Due to the high degree of non-linearity of both systems, the models are re-linearized at each time step and a linear, delta MPC formulation is used.
The controller is implemented using the quadratic program solver \qpoases{}, and a \cpp{} implementation is used to evaluate the computational cost of each control approach.
The non-cooperative controller exhibited a significantly reduced computation time relative to the centralized controller (25\% and 40\% lower for the parallel and serial configurations, respectively), while the cooperative controller did not significantly reduce the computation time.
For the parallel configuration, both distributed and centralized controllers had identical control performance.
For the serial configuration, only the cooperative controller achieved similar performance to the centralized approach; the non-cooperative controller demonstrated a 9\% reduction in the minimum surge control distance reached in the downstream compressor.
\end{abstract}

\begin{keyword}
  Distributed mpc, anti-surge control, nonlinear mpc, compressor modeling, variable speed drive
\end{keyword}

\end{frontmatter}
%===============================================================================

\section{Introduction}
\input{intro.tex}

\section{Modelling \& Simulation}
\input{modelling.tex}

\section{Model Predictive Control Formulation}
\input{mpc.tex}

\section{Simulation Results}
\input{results.tex}

\section{Conclusion}
% \input{conclusion.tex}

\bibliography{end/MasterThesis.bib}
\end{document}
